---
title: "Survey"
output: pdf_document
---

```{r}
# library for data wrangling and ggplot
library(tidyverse)

# read in DT survey answers
survey = read.csv("DTsurvey.csv")

# list of grades for condition to compare to
grades = c("A+","A","A-","B+","B","B-","C+","C","C-")

# initialize empty vector
# nongrades = NULL
# grades = NULL

# total sample size
samplesize = nrow(survey)

# dataframe containing students that entered their postal codes
postalcodes = survey[!(is.na(survey$postal.code)),]

#nongamers = survey[survey$gamer.yes.or.no.=="no",]

# students that didn't fill in average grades
# nagrades = survey[is.na(survey$avg.lettergrade),]

# filled grades
# filledgrades = survey[!(is.na(survey$avg.lettergrade)), ]

# took out weird answers that students put and combined with NA grades
nagrades = survey[!(survey$avg.lettergrade %in% grades),]

# students that properly filled in grades
propergrades = survey %>% 
  filter_at(vars("avg.lettergrade"),any_vars(. %in% grades))

# gamers with filled in grades
gamers = propergrades[propergrades$gamer.yes.or.no. == "yes",]

# nongamers with filled in grades
nongamers = propergrades[propergrades$gamer.yes.or.no. == "no",]

# 106 gamers that properly filled grades
nrow(gamers)

# 8 non gamers that properly filled grades
nrow(nongamers)

# counts of nongamers grades
nongamers_counts = as.data.frame(table(nongamers$avg.lettergrade))

# counts of gamers grades 

gamers_counts = as.data.frame(table(gamers$avg.lettergrade))

# adding a column of counts
gamers$count = 1

# fixed error 

gamers[7,"time.played"] = "16+"

# group up average grade and time played
grouped_gamers_timeplayed = gamers %>% select(avg.lettergrade,time.played,count) %>%
  group_by(avg.lettergrade,time.played) %>% summarise(Freq = sum(count))

# student didn't specify time played
grouped_gamers_timeplayed[23,]

# remove student with no time specificed 
grouped_gamers = grouped_gamers_timeplayed[-23,]

# remove NA time played from gamers
gamers_plot = gamers[-5,]

# reorder the levels of letter grades for gamers

gamers_plot$avg.lettergrade = factor(gamers_plot$avg.lettergrade, levels = grades)

# reorder the levels of time.played for gamers
gamers_plot$time.played = factor(gamers_plot$time.played, 
                                 levels = c("1 to 5", "6 to 10", "10 to 15", "16+"))

# changed the error from 10 to 15 to 11 to 15
gamers_plot$time.played = gsub("10 to 15", "11 to 15", gamers_plot$time.played)
```



```{r}
# library containing unique color values 
library(RColorBrewer)
# plot with points of gamers letter grades and frequency grouped by time played

(p1 = ggplot(grouped_gamers, aes(x = avg.lettergrade, y = Freq, 
                                 color = time.played)) + geom_point())

# bar plot of gamers with letter grades and frequency grouped by time played
(p2 = ggplot(gamers_plot, aes(x = avg.lettergrade, fill = time.played)) + 
    geom_bar(position = "dodge") + scale_fill_brewer(palette = "RdBu") + 
    labs(x = "Letter Grade", y = "Number of Students", 
         title = "DT Students Letter Grades and Time Spent Gaming") + 
    guides(fill = guide_legend(title = "Time Spent Gaming")))
```

```{r}
# change all letter grades to just a whole letter
gamers_plot$avg.lettergrade = gsub("[\\+\\-]","",gamers_plot$avg.lettergrade)

(p3 = ggplot(gamers_plot, aes(x = avg.lettergrade, fill = time.played)) + 
    geom_bar(position = "dodge") + scale_fill_brewer(palette = "RdBu") + 
    labs(x = "Letter Grade", y = "Number of Students", 
         title = "DT Students Letter Grades and Time Spent Gaming") + 
    guides(fill = guide_legend(title = "Time Spent Gaming")))
```

```{r}
# number of students per time played

freq_timeplayed = 
  gamers_plot %>% select(time.played,count) %>% group_by(time.played) %>% summarise(freq = sum(count))
```


```{r}
# change , in one of the answers to a /

gamers_plot$most.played.game = gsub(",","/",gamers_plot$most.played.game)


# frequency of games played

mostgamesplayed = gamers_plot %>% select(most.played.game,count) %>% 
  group_by(most.played.game) %>% summarise(freq = sum(count))

# proportion of the gamer students of this survey that play these games
mostgamesplayed$prop = mostgamesplayed$freq/nrow(gamers_plot)

# top games sorted by most popular games in the school
top_games_sorted = mostgamesplayed %>% arrange(desc(freq))
```

```{r}
# drop postal codes since about half of students didn't fill in
gamers_plot = gamers_plot %>% select(-postal.code)
```

```{r}
library(survey)


```


# for DT surveys: 

## bias 

- students might not know what being a casual and competitive gamer is, some students 
put down themselves down as a competitive player when their favourite game is a 
casual game

```{r}
# competitive gamers but with casual games
gamers[c(58,59,66,80),c(10,11)]
```


- a lot of students didn't want to or know what their postal codes are

```{r}
# number of students who didn't put their postal code down
nrow(survey)-nrow(postalcodes)
```

```{r}
# students that wrote don't know or no or wrote a wrong postal code
postalcodes[c(7,10,13,28,34),"postal.code"]
```


- some students didn't want to put in their grades, also students could potentially 
lie

```{r}
# students that didn't put down grades or wrote something else
nagrades
```


- some nongamers wrote down a most played game even though they said they aren't a gamer


```{r}
# nongamers playing games
nongamers[c(4,7),]
```


- some students wrote a couple of most played games, didn't choose just one

```{r}
# students with multiple most played games
grep("/",top_games_sorted$most.played.game,value = TRUE)
```


- some students play both on the weekdays and weekends so they circled both, 
should've added both as an option

```{r}
gamers_plot[gamers_plot$weekday.or.weekend=="both",]
```


- some students misinterpreted single or multiplayer question as playing by 
themselves or with friends 

```{r}
gamers_plot[c(78,87,94,105),c("single.or.multi","most.played.game")]
```

- should have included both as an answer for the single or multiplayer question 
as some games have both

```{r}
# just one gamer with both in single or multiplayer question
gamers[gamers$single.or.multi == 'both',]
```

## limitations

- survey asks for 6 to 10 or 10 to 15, should've been 11 to 15 but not much 
of a limitation because students generally know the range of hours, they play 
for example, if they think they play less than 10, they'll put down 6 to 10, if 
they think they play more than 10 but less than 16+ then they'll put 10 to 15

- ran into an issue where the term just began thus no test marks or grades were 
available to me thus have to add in alternative questions but forgot to add in 
questions about age and gender but added in postal codes and average grades


- grades at DT for gr8 were beginning, developing, applying, extending
(C-, C, B, A)

- some students wrote in between so i did this,

beginning/developing = C-,
developing/applying = B-, 
applying/extending = A-



