---
title: "Stat410Survey"
author: "Rajvir Sangha, 301301767"
date: "14/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Title page

# Thank you page for the teachers who made this survey possible

# Abstract

# Introduction (Includes questions of interest)

# Data description

# Some visuals

# Methods

# Results

# Conclusion

# Reference 

@data{AB2/4LXJQS_2019,
author = {DMTI Spatial Inc.},
publisher = {Abacus Data Network},
title = {{CanMap Postal Code Suite, v2019.3}},
year = {2019},
version = {V1},
doi = {11272.1/AB2/4LXJQS},
url = {https://hdl.handle.net/11272.1/AB2/4LXJQS}
}



```{r message=FALSE, warning=FALSE}
# Import Libraries
library(plyr)
library(survey)
library(ggplot2)
library(tidyverse)
library(patchwork)
library(gmodels)
library(vcd)
library(data.table)
```


```{r}
# Reading the csv file, total n=56 students
data <- read.csv(file = "Survey Data - SUM.csv", header = T)

# Subset Gamer students, n=35
gamerData <- subset(data, Gamer.Y.N.==1)

# Subset Non-Gamer students, n=21
nongamerData <- subset(data, Gamer.Y.N.==0)

# Gives an idea of the data
glimpse(data)
```





```{r}
count(data, c('Gender'))
data %>% count(Gamer.Y.N.)
```



```{r echo=FALSE}
Fig.1 <- (ggplot(data, aes(x = ID, y = Avg.lettergrade, color=Gender)) 
      + geom_point(shape=18,size=2.5) 
      + labs(x = "Students", y = "Letter Grades", title = "Students VS. Letter Grades", 
             subtitle = "56 Frankhurt Secondary students' letter grades",tag = "Fig. 1")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 15))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      )
Fig.2 <- (ggplot(gamerData, aes(x = ID, y = Age, color=Gender)) 
      + geom_point(shape=15,size=2) 
      + labs(x = "Students", y = "Age", title = "Gamer Students VS. Ages", 
             subtitle = "35 Frankhurt Secondary gamer students' ages",tag = "Fig. 2")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 15))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      )
Fig.3 <- (ggplot(gamerData, aes(x = ID, y = Time.played, color=Gender)) 
      + geom_point(shape=16,size=2.5) 
      + labs(x = "Students", y = "Time played", title = "Gamer Students VS. Time played", 
             subtitle = "35 Frankhurt Secondary gamer students' time played",tag = "Fig. 3")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 15))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      + scale_y_discrete(limits=c("1 to 5","6 to 10","11 to 15","16 or more"))
      )
Fig.4 <- (ggplot(gamerData, aes(x = ID, y = Weekdays.Weekend, color=Gender)) 
      + geom_point(shape=17,size=2.5) 
      + labs(x = "Students", y = "Weekdays/Weekend", title = "Gamer Students VS. Weekdays/Weekend", 
             subtitle = "35 Frankhurt Secondary gamer students play on weekdays or weekend",tag = "Fig. 4")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 12))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      )
Fig.5 <- (ggplot(gamerData, aes(x = ID, y = Before.After.HW., color=Gender)) 
      + geom_point(shape=18,size=2.5) 
      + labs(x = "Students", y = "Time played", title = "Gamer Students VS. Before/After Homework", 
             subtitle = "35 Frankhurt Secondary gamer students play before or after homework",tag = "Fig. 5")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 15))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      )
Fig.6 <- (ggplot(gamerData, aes(x = ID, y = Casu.Comp, color=Gender)) 
      + geom_point(shape=19,size=2.5) 
      + labs(x = "Students", y = "Casual/Competitive", title = "Gamer Students VS. Casual/Competitive Type", 
             subtitle = "35 Frankhurt Secondary gamer students are casual or competitive players",tag = "Fig. 6")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 13.5))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      )
Fig.7 <- (ggplot(gamerData, aes(x = ID, y = Platform, color=Gender)) 
      + geom_point(shape=20,size=2.5) 
      + labs(x = "Students", y = "Platform", title = "Gamer Students VS. Platform", 
             subtitle = "35 Frankhurt Secondary gamer students' preferred platform",tag = "Fig. 7")
      + theme(axis.title.x = element_text(vjust = 0, size = 15),axis.title.y = element_text(vjust = 2, size = 15))
      + theme(axis.title = element_text(size = 15, color = "firebrick", face = "italic"))
      + theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1, size = 5))
      + theme(legend.title = element_text(color = "chocolate",size = 11, face = "bold"))
      + theme(panel.grid = element_blank())
      + theme(panel.background = element_rect(fill = "gray97"))
      + scale_color_manual(values = c("skyblue","pink"))
      + scale_y_discrete(limits=c("Mobile","PC","Console"))
      )

```







```{r}
# Figure 1
Fig.1

# Using the subset of gamer students called gamerData
# Figures 2 through Figures 7 
(Fig.2 / Fig.3); (Fig.4 / Fig.5); (Fig.6 / Fig.7)

```





Impressions on the dataset: 

Fig.1 indicates that the majority of the students' grades lie in A's and B' and the few who are scoring C's are mainly Men.

Fig.2 indicates that most of the students sampled are ages 16 and 17.

Fig.3 indicates that there are only Men in the "16 or more" time played category and that most girls prefer to play "1 to 5" hours.

Fig. 4 indicates that most gamers play on the weekend.

Fig. 5 indicates that most gamers play after their homework is finished. 

Fig. 6 indicates that most gamers are casual players.

Fig. 7 indicates that most of the gamers prefer console over PC and mobile. 





```{r}

gamerData$count =1
cont.df = as.data.frame(gamerData %>% select(Avg.lettergrade,Time.played,count) %>% group_by(Avg.lettergrade,Time.played) %>% summarise(freq = sum(count)))
cont.df

TimeGradeTable <- xtabs(formula = freq~Time.played+Avg.lettergrade, data=cont.df)
TimeGradeTable

CrossTable(gamerData$Avg.lettergrade,gamerData$Gender)

oddsRat <- oddsratio(TimeGradeTable, log=FALSE)
summary(oddsRat)

```






#### Do gamers perform better than non-gamers
```{r}
# Creates the df for the Gamer data 
gamerData$count =1
cont.df = as.data.frame(gamerData %>% select(Avg.lettergrade,Gamer.Y.N.,count) %>% group_by(Avg.lettergrade,Gamer.Y.N.) %>% summarise(freq = sum(count)))

# Creates the table and we add 0.5 to every value due to Haldane-Anscombe correction
gamerGradeTable <- xtabs(formula = freq~Gamer.Y.N.+Avg.lettergrade, data=cont.df)
gamerGradeTable <- gamerGradeTable[,]+0.5
gamerGradeTable

# Creates the df for the Non-Gamer data 
nongamerData$count =1
cont.df = as.data.frame(nongamerData %>% select(Avg.lettergrade,Gamer.Y.N.,count) %>% group_by(Avg.lettergrade,Gamer.Y.N.) %>% summarise(freq = sum(count)))

# Creates the table and we add 0.5 to every value due to Haldane-Anscombe correction
nongamerGradeTable <- xtabs(formula = freq~Gamer.Y.N.+Avg.lettergrade, data=cont.df)
nongamerGradeTable <- nongamerGradeTable[,]+0.5
nongamerGradeTable

# Calculating OR 
OR_AB = (gamerGradeTable[1]*nongamerGradeTable[2])/(gamerGradeTable[2]*nongamerGradeTable[1])
OR_AB
OR_AC = (gamerGradeTable[1]*nongamerGradeTable[3])/(gamerGradeTable[3]*nongamerGradeTable[1])
OR_AC
OR_BC = (gamerGradeTable[2]*nongamerGradeTable[3])/(gamerGradeTable[3]*nongamerGradeTable[2])
OR_BC

# Calculating the CI 
ci_AB <- exp(log(OR_AB) + c(-1,1) * qnorm(0.975) * sqrt( (1/gamerGradeTable[1]) + (1/gamerGradeTable[2]) +
                                                (1/nongamerGradeTable[1]) + (1/nongamerGradeTable[2]) ))
ci_AB
ci_AC <- exp(log(OR_AC) + c(-1,1) * qnorm(0.975) * sqrt( (1/gamerGradeTable[1]) + (1/gamerGradeTable[3]) +
                                                (1/nongamerGradeTable[1]) + (1/nongamerGradeTable[3]) ))
ci_AC
ci_BC <- exp(log(OR_BC) + c(-1,1) * qnorm(0.975) * sqrt( (1/gamerGradeTable[2]) + (1/gamerGradeTable[3]) +
                                                (1/nongamerGradeTable[2]) + (1/nongamerGradeTable[3]) ))
ci_BC



```



























